---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# blendR
[![DOI](http://joss.theoj.org/papers/10.21105/joss.00886/status.svg)](https://doi.org/10.21105/joss.00886)

The goal of blendR is to provide statistically valid estimators of total (and standard errors) when blending a non-probability sample with a probability sample. The two samples are considered to follow capture-recapture methodology, with the capture sample being the non-probability sample and the recapture sample being the probability sample. This package is based upon research by Liu et al (2017), Breidt, Opsomer, and Huang (2018), and dissertation research by the package author. Additional estimators will be released in future versions.

These estimators are important and currently used by Texas Parks and Wildlife to estimate the total number of Red Snapper fish caught. Combining data sources is an important research area due to the prevalence of big data in both industry and academia. These estimators can easily extend to other areas of interest, for example, the internet of things, insurance claims, and estimation of the death toll due to a natural disaster.

## Installation

You can install blendR from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("williamsbenjamin/blendR")
```

## Example

An example using data from a capture-recapture sampling program in 2016 by Texas Parks and Wildlife
Captains could voluntarily self-report (via a smartphone app) about their catch of Red Snapper fish (non-probability sample) and could be sampled in a dockside intercept sample (probability sample). The self-reports are the capture sample and the dockside intercept is the recapture, probability sample.

```{r example}

library(tibble)
library(blendR)

## Dataset for boats sampled in the dockside intercept, if their captains also self-reported, that data included as well

red_snapper_sampled

## Dataset for the self-reported boats

self_reports 

s_design <- survey::svydesign(id = ~psu,
                              strat = ~stratum,
                              prob = ~prob,
                              nest = T,
                              data = red_snapper_sampled)

t_p(data = red_snapper_sampled,
    recapture_total = number_caught_ps,
    captured = captured_indicator,
    survey_design = s_design,
    capture_units = nrow(self_reports))
```
