---
title: "BlendR: Combining a Probability and a Non-Probability Sample in a Capture-Recapture Setting"
author: "Benjamin Williams"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package provides several estimators of total for combining a non-probability sample with a probability sample.  In general, probability samples are preferred to non-probability samples because the sampling variance of the estimators calculated from probability samples can be determined using standard sampling theory. Even non-sampling errors, such as non-response bias, may be easier to assess and mitigate for probability samples. The primary disadvantage of non-probability samples is the potential for biased estimation stemming from undercoverage and a lack of representativeness in the samples. Without external sources of information, these sample deficiencies cannot be detected.

In reality, it is usually easier to obtain a non-probability sample than a probability sample. For example, a frame may not be available, which complicates the selection of a probability sample. A non-probability sample, such as one using data from volunteers, does not require an expensive nonresponse follow-up. The larger the sample, the more information it may contain. This is an attractive option for analysts working with limited resources while studying elusive populations. As a result, statisticians have begun to investigate methods for improving estimation using data from non-probability samples.




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
